---
title: "IAQF Trading Strategies"
output: pdf_document
---

```{r echo=FALSE}
setwd("C:/_UCLA/IAQF")

########BLOOMBERG DATA#############
library(readxl)
suppressMessages(library(xts))
read_excel_allsheets <- function(filename) {
  sheets <- readxl::excel_sheets(filename)
  x <-    lapply(sheets, function(X) readxl::read_excel(filename, sheet = X,skip = 1))
  names(x) <- sheets
  x
}
suppressWarnings(data <- read_excel_allsheets("Data_FixedIncome_IAQF.xlsx"))


#10 year yield data
suppressWarnings(dataNew <- read_excel_allsheets("10YearBondYield.xlsx"))
govt.10year <- xts(dataNew$Sheet2$PX_LAST,order.by = as.Date(dataNew$Sheet2$Date))

# 1 year yield data
Tbill.1Y <- read.csv("DGS1.csv")
Tbill.1Y[Tbill.1Y$DTB1YR == '.',"DGS1"] <- NA
Tbill.1Y <- xts(Tbill.1Y$DGS1,as.Date(Tbill.1Y$DATE))
Tbill.1Y <- na.approx(Tbill.1Y)
storage.mode(Tbill.1Y) <- "numeric"

#20 year yield data
govt.20Y <- read.csv("DGS20.csv")
govt.20Y[govt.20Y$DGS20 == '.',"DGS20"] <- NA
govt.20Y <- xts(govt.20Y$DGS20,as.Date(govt.20Y$DATE))
govt.20Y <- na.approx(govt.20Y)
storage.mode(govt.20Y) <- "numeric"
```

#Strategy 1 - Long 10 Year Government Bonds and short 1 year bonds  

##Levels  
For levels, we take the two and find the difference in their returns  
```{r echo=FALSE}
#Yield diff for govt 10 year government bonds
govt.10Year.diff <- diff(govt.10year)[-1,]

#Price diff for govt 1 year T bills
Tbill.1Y.diff <- diff(Tbill.1Y)[-1] 

Govt.10Yr1Yr <- na.omit(merge.xts(govt.10Year.diff,Tbill.1Y.diff))
Govt.10Yr1Yr.Levels <- Govt.10Yr1Yr[,1] - Govt.10Yr1Yr[,2]
colnames(Govt.10Yr1Yr.Levels) <- c("10Yr1YrReturns")
write.csv(as.matrix(Govt.10Yr1Yr.Levels),"Strategy1_1Y10Y.csv")

#plot(Govt.10Yr1Yr.Levels,main="Overall Levels of 10 Yr return - 1 yr return")
plot(Govt.10Yr1Yr.Levels['2004-06/2006-08'],main="2004-2006 Hike Levels of 10 Yr return - 1 yr return")
#plot(Govt.10Yr1Yr.Levels['2007-03/2009-07'],main="Financial Crisis Levels of 10 Yr return - 1 yr return")
#plot(Govt.10Yr1Yr.Levels['2015-01/2017-02'],main="Latest Levels of 10 Yr return - 1 yr return")
```
In standalone, the difference in returns between 10 year and 1 year varies between -0.1 and 0.1


##Rolling Correlation
```{r echo=FALSE}
#Rolling Correlation with daily yield diffs (returns)
GovtD.10Yr1Yr.Cor3M<- rollapply(Govt.10Yr1Yr,60,function(x) cor(x[,1],x[,2]),by.column = FALSE)
plot(GovtD.10Yr1Yr.Cor3M['2004-06/2006-08'],main="3 month Rolling correlation between 10 yr and 1 year daily return")

#Rolling correlation with weekly yield diffs(returns)
GovtW.10Yr1Yr <- apply.weekly(1+Govt.10Yr1Yr/100,function(x) apply(x,2,prod))-1
GovtW.10Yr1Yr.Cor3M<- rollapply(GovtW.10Yr1Yr,12,function(x) cor(x[,1],x[,2]),by.column = FALSE)
plot(GovtW.10Yr1Yr.Cor3M['2004-06/2006-08'],main="3 month Rolling correlation between 10 yr and 1 year weekly return")
```

The 3 Month rolling correlation (daily and weekly returns) are consistently positive over the rate hike period

#Strategy 2 - Long 1 year returns, 2 Short 10 year returns, 1 long 20 year returns  

##Levels  
For levels, we find the net value of returns on a daily basis  
```{r echo=FALSE}
#Yield diff for govt 20 year government bonds
govt.20Y.diff <- diff(govt.20Y)[-1,]

Govt.20Yr10Yr1Yr <- na.omit(merge.xts(govt.20Y.diff,govt.10Year.diff,Tbill.1Y.diff))
Govt.20Yr10Yr1Yr.Levels <- Govt.20Yr10Yr1Yr[,1] - 2*Govt.20Yr10Yr1Yr[,2] + Govt.20Yr10Yr1Yr[,3] 
colnames(Govt.20Yr10Yr1Yr.Levels) <- c("20Yr10Yr1YrReturns")
write.csv(as.matrix(Govt.20Yr10Yr1Yr.Levels),"Strategy2_1Y10Y20Y.csv")

#plot(Govt.20Yr10Yr1Yr.Levels,main="Overall 20Y - 2*10Y + 1Y")
plot(Govt.20Yr10Yr1Yr['2004-06/2006-08'],main="2004-2006 -> 20Y -2 * 10Y + 1Y")
#plot(Govt.20Yr10Yr1Yr.Levels['2007-03/2009-07'],main="Financial Crisis -> 20Y -2 * 10Y + 1Y")
#plot(Govt.20Yr10Yr1Yr.Levels['2015-01/2017-02'],main="Latest Levels -> 20Y -2 * 10Y + 1Y")
```
In standalone, the difference in return of '20Y -2 * 10Y + 1Y' strategy varies between -0.1 and 0.1


#Strategy 3 - AAA Bonds - BBB Bonds levels  
##Levels  
```{r echo=FALSE}
#AAA Bond yields
AAA.10yr <- read.csv("AAABondYield.csv")
AAA.10yr[AAA.10yr$BAMLC0A1CAAAEY == '.',"BAMLC0A1CAAAEY"] <- NA
AAA.10yr <- xts(AAA.10yr$BAMLC0A1CAAAEY,as.Date(AAA.10yr$DATE))
AAA.10yr <- na.approx(AAA.10yr)
storage.mode(AAA.10yr) <- "numeric"
AAA.10yr.diff <- diff(AAA.10yr)[-1]

#BBB Bond yields
BBB.10yr <- read.csv("BBBBondYield.csv")
BBB.10yr[BBB.10yr$BAMLC0A4CBBBEY == '.',"BAMLC0A4CBBBEY"] <- NA
BBB.10yr <- xts(BBB.10yr$BAMLC0A4CBBBEY,as.Date(BBB.10yr$DATE))
BBB.10yr <- na.approx(BBB.10yr)
storage.mode(BBB.10yr) <- "numeric"
BBB.10yr.diff <- diff(BBB.10yr)[-1]

AAA.BBB <- na.omit(merge.xts(AAA.10yr.diff,BBB.10yr.diff))
AAA.BBB.Levels <- AAA.BBB[,1] - AAA.BBB[,2] 
colnames(AAA.BBB.Levels) <- "AAABBBReturns"
write.csv(as.matrix(AAA.BBB.Levels),"Strategy3_AAABBB.csv")


#plot(AAA.BBB.Levels)
plot(AAA.BBB.Levels['2004-06/2006-08'],main="2004-2006 Hike Levels of AAA return - BBB return")
```
The Levels of returns are very low during the rate hike period. 

