---
title: "IAQF"
author: "Fixed Income"
output: word_document
---

```{r echo=FALSE}
########################################
########################################
###STEPS:Press ALT+0 TO COLLAPSE. THEN NAVIGATE TO NECESSARY SECTION
########################################
########################################
```
##DATA RETRIEVAL
```{r echo=FALSE}
setwd("C:/_UCLA/Personal/IAQF")
#libraries
library(readxl)
suppressMessages(library(xts))
suppressMessages(library(dplyr))
suppressMessages(library(quantmod))
suppressMessages(library(xtable))
suppressMessages(library(lubridate))

##GET BLOOMBERG AND FRED DATA
read_excel_allsheets <- function(filename) {
  sheets <- readxl::excel_sheets(filename)
  x <-    lapply(sheets, function(X) readxl::read_excel(filename, sheet = X,skip = 1))
  names(x) <- sheets
  x
}
suppressWarnings(data <- read_excel_allsheets("Data_FixedIncome_IAQF.xlsx"))
suppressWarnings(dataNew <- read_excel_allsheets("IAQF_Data.xlsx"))

suppressWarnings(dataNew <- read_excel_allsheets("10YearBondYield.xlsx"))
govt.10year <- xts(dataNew$Sheet2$PX_LAST,order.by = as.Date(dataNew$Sheet2$Date))
govt.10Year.daily <- diff(govt.10year)/100
colnames(govt.10Year.daily) <- "10YrGovtRet"
govt.10Year.Weekly <- apply.weekly(1+govt.10Year.daily,prod)-1
colnames(govt.10Year.Weekly) <- "10YrGovtRet"
```


```{r echo=FALSE}
#All hike periods
hikePeriods <- matrix(c("1983-03-31","1984-08-09","1988-03-30","1989-05-17","1994-02-04","1995-02-01","1999-06-30","2000-05-16","2004-06-30","2006-06-29","2006-06-29","2009-06-30","2009-07-01","2017-02-01"),ncol=2,byrow = TRUE)
hikePeriodNames <- c("83_84","88_89","94_95","99_00","04_06")
AllPeriods <- c(hikePeriodNames,"Recession","Now")

#calculate return of data provided
hikePeriodData <- function(data.returns,basedata){
  data.full <- na.omit(merge.xts(basedata,data.returns))

  data.HikePeriods <- lapply(1:nrow(hikePeriods),function(x){
    period <- paste0(hikePeriods[x,1],"/",hikePeriods[x,2])
    data.full[period]
  })
  
  names(data.HikePeriods) <- AllPeriods
  return(data.HikePeriods)
}

#Get the necessary stats
Necessarystats <- function(data,freq="Y"){
    lapply(data,function(x){
        if(nrow(x) > 0){
          means <- apply(x,2,mean)
          sds <- apply(x,2,sd)
          noOfYrs <- as.numeric(difftime(max(index(x)),min(index(x)),units = "weeks")/52.25)
          annualizedReturnsAvg <- sapply(1+x,function(y){mean(apply.yearly(y,prod))})-1
          
          multipler = 1
          if(freq=="D"){
            multiplier = sqrt(250)
          }
          else if(freq=="W"){
            multiplier = sqrt(52)
          }
          else if(freq=="M"){
            multipler = sqrt(12)
          }
          
          annualizedSd <- sds*multiplier
          sharpeRatio <- annualizedReturnsAvg/annualizedSd
          rbind(means,sds,annualizedReturnsAvg,annualizedSd,sharpeRatio)
        }
    })
}

#Get Weekly data
weeklyData <- function(data){
  lapply(data,function(x){
    if(nrow(x)>0){
      y1 <- apply.weekly(1+x[,1],prod)-1
      y2 <- apply.weekly(1+x[,2],prod)-1
      cbind(y1,y2)
    }
  })
}

#Calculating rolling correlation
rollingCorrelations <- function(data,RequiredFreq='D'){
  Rollfreq <- 1
  if(RequiredFreq=='D'){
    Rollfreq  <- 60
  }
  else if(RequiredFreq=='W'){
    Rollfreq <- 12
  }
  else if(RequiredFreq=='M'){
    Rollfreq <-  3
  }
  lapply(data,function(x){
      rollapply(x,Rollfreq,function(x) cor(x[,1],x[,2]),by.column = FALSE)
    })
}

```

##BARCLAYS AGGREGATE 

```{r echo=FALSE}
#Get Data
BarcTotalAggr <- xts(data$`Barclays US Total Aggregate`[,c(2,3)],data$`Barclays US Total Aggregate`$Date)

#Get data returns in hike periods
BarcTotalAggr.Daily <- diff(BarcTotalAggr[,2])/100
colnames(BarcTotalAggr.Daily) <- "BarcAggr"
BarcTotalAggr.HikePeriods.Daily <- hikePeriodData(BarcTotalAggr.Daily,govt.10Year.daily)
#Get mean, variance, annualized returns
BarcTotalAggr.Stats <- Necessarystats(BarcTotalAggr.HikePeriods.Daily,"D")
BarcTotalAggr.Stats

#Get complete correlations during this period
BarcTotalAggr.Corr <- lapply(BarcTotalAggr.HikePeriods.Daily,cor)
BarcTotalAggr.Corr

#Weekly 3 month rolling correlation
BarcTotalAggr.Weekly <- apply.weekly(1+BarcTotalAggr.Daily,prod)-1
BarcTotalAggr.HikePeriods.Weekly <- hikePeriodData(BarcTotalAggr.Weekly,govt.10Year.Weekly)
BarcTotalAggr.RollCorr <- rollingCorrelations(BarcTotalAggr.HikePeriods.Weekly[-1],'W')

plot(do.call(rbind,BarcTotalAggr.RollCorr[c("04_06","Recession","Now")]),main="Rolling Correlation Barclays Aggregate")
abline(v = as.POSIXct.Date(as.Date(hikePeriods[5,2])), col = 'blue', lty = 3, lwd = 2)
abline(v = as.POSIXct.Date(as.Date(hikePeriods[6,2])), col = 'blue', lty = 3, lwd = 2)
text(x=1120724623,y=0.5316487,"Rate Hike",col = "Red")
text(x=1190809736,y=0.4698893,"Recession",col = "Red")
text(x=1325382051,y=0.5402662,"Now",col = "Red")
```


##GOVT INFLATION INDEXED 10 year
```{r echo=FALSE}
GovtII10 <- xts(data$GovtII10$PX_MID,data$GovtII10$Date)

#Get data returns in hike periods
GovtII10.Daily <- diff(GovtII10)/100
colnames(GovtII10.Daily) <- "GovtII10"
GovtII10.HikePeriods.Daily <- hikePeriodData(GovtII10.Daily,govt.10Year.daily)

#Get mean, variance, annualized returns
GovtII10.Stats <- Necessarystats(GovtII10.HikePeriods.Daily,"D")
GovtII10.Stats

#Get complete correlations during this period
GovtII10.Corr <- lapply(GovtII10.HikePeriods.Daily,cor)
GovtII10.Corr

GovtII10.HikePeriods.Weekly <- weeklyData(GovtII10.HikePeriods.Daily)
GovtII10.RollCorr <- rollingCorrelations(Filter(Negate(is.null), GovtII10.HikePeriods.Weekly),"W")

plot(do.call(rbind,GovtII10.RollCorr[c("04_06","Recession","Now")]),main="Rolling Correlation Govt10 Inflation Indexed bonds")
abline(v = as.POSIXct.Date(as.Date(hikePeriods[5,2])), col = 'blue', lty = 3, lwd = 2)
abline(v = as.POSIXct.Date(as.Date(hikePeriods[6,2])), col = 'blue', lty = 3, lwd = 2)
text(x=1120724623,y=0.002514136,"Rate Hike",col = "Red")
text(x=1210809736,y=0.1224832,"Recession",col = "Red")
text(x=1325382051,y=0.005892442,"Now",col = "Red")
```


##GOVT INFLATION INDEXED 5 year
```{r echo=FALSE}
GovtII5 <- xts(data$GovtII5$PX_MID,data$GovtII5$Date)
GovtII5.Daily <- diff(GovtII5)/100
colnames(GovtII5.Daily) <- "GovtII5"

#Get data returns in hike periods
GovtII5.HikePeriods.daily <- hikePeriodData(na.omit(GovtII5.Daily),govt.10Year.daily)

#Get mean, variance, annualized returns
GovtII5.Stats <- Necessarystats(GovtII5.HikePeriods.daily,freq="D")
GovtII5.Stats

#Get complete correlations during this period
GovtII5.Corr <- lapply(GovtII5.HikePeriods.daily,cor)
GovtII5.Corr

GovtII5.HikePeriods.Weekly <- weeklyData(GovtII5.HikePeriods.daily)
GovtII5.RollCorr <- rollingCorrelations(Filter(Negate(is.null), GovtII5.HikePeriods.Weekly),"W")

plot(do.call(rbind,GovtII5.RollCorr[c("04_06","Recession","Now")]),main="Rolling Correlation Govt 5year Inflation Indexed bonds")
abline(v = as.POSIXct.Date(as.Date(hikePeriods[5,2])), col = 'blue', lty = 3, lwd = 2)
abline(v = as.POSIXct.Date(as.Date(hikePeriods[6,2])), col = 'blue', lty = 3, lwd = 2)
```

##Govt 30 YEAR
```{r echo=FALSE}
Govt30 <- xts(data$Govt30$PX_MID,data$Govt30$Date)
#Get data returns in hike periods
Govt30.Daily <- diff(Govt30)/100
Govt30.HikePeriods.Daily <- hikePeriodData(na.omit(Govt30.Daily),govt.10Year.daily)

#Get mean, variance, annualized returns
Govt30.Stats <- Necessarystats(Govt30.HikePeriods.Daily,"D")
Govt30.Stats

#Get complete correlations during this period
Govt30.Corr <- lapply(Govt30.HikePeriods.Daily,cor)
Govt30.Corr

Govt30.HikePeriods.Weekly <- weeklyData(Govt30.HikePeriods.Daily)
Govt30.RollCorr <- rollingCorrelations(Filter(Negate(is.null), Govt30.HikePeriods.Weekly),"W")

plot(do.call(rbind,Govt30.RollCorr[c("04_06","Recession","Now")]),main="Rolling Correlation Govt 30 bonds")
abline(v = as.POSIXct.Date(as.Date(hikePeriods[5,2])), col = 'blue', lty = 3, lwd = 2)
abline(v = as.POSIXct.Date(as.Date(hikePeriods[6,2])), col = 'blue', lty = 3, lwd = 2)

```


##1Y-10Y yield curve check vs 1Y-10Y-20Y vol check vs Credit check
```{r echo=FALSE}
suppressWarnings(sp500data <- read_excel_allsheets("SP500_Price.xlsx"))
sp500 <- xts(sp500data$Sheet1$PX_LAST,order.by = as.Date(sp500data$Sheet1$Date))
sp500.daily <- dailyReturn(sp500)
colnames(sp500.daily) <- "SP500"
Strategy1_1Y10Y <- read.csv("Strategy1_1Y10Y.csv",stringsAsFactors = FALSE)
Strat1_1Y10Y <- xts(Strategy1_1Y10Y[,2]/100,as.Date(Strategy1_1Y10Y[,1]))
colnames(Strat1_1Y10Y) <- "1Y10Y"

Strat1_1Y10Y.HikePeriods.Daily <- hikePeriodData(sp500.daily,Strat1_1Y10Y)

Strat1_1Y10Y.Stats <- Necessarystats(Strat1_1Y10Y.HikePeriods.Daily,"D")
Strat1_1Y10Y.Stats

#Get complete correlations during this period
Strat1_1Y10Y.Corr <- lapply(Strat1_1Y10Y.HikePeriods.Daily,cor)

Strat1_1Y10Y.HikePeriods.Weekly <- weeklyData(Strat1_1Y10Y.HikePeriods.Daily)
Strat1_1Y10Y.RollCorr <- rollingCorrelations(Filter(Negate(is.null), Strat1_1Y10Y.HikePeriods.Weekly),"W")

```


```{r echo=FALSE}
Strategy2_Vol <- read.csv("Strategy2_1Y10Y20Y.csv",stringsAsFactors = FALSE)
Strat2_Vol <- xts(Strategy2_Vol[,2]/100,as.Date(Strategy2_Vol[,1]))
colnames(Strat2_Vol) <- "VolCheck"

Strat2.HikePeriods.Daily <- hikePeriodData(Strat2_Vol,govt.10Year.daily)

Strat2.Stats <- Necessarystats(Strat2.HikePeriods.Daily,"D")
Strat2.Stats

#Get complete correlations during this period
Strat2.Corr <- lapply(Strat2.HikePeriods.Daily,cor)

Strat2.HikePeriods.Weekly <- weeklyData(Strat2.HikePeriods.Daily)
Strat2.RollCorr <- rollingCorrelations(Filter(Negate(is.null), Strat2.HikePeriods.Weekly),"W")
```

```{r echo=FALSE}
Strategy3_Credit <- read.csv("Strategy3_AAABBB.csv",stringsAsFactors = FALSE)
Strat3_Credit <- xts(Strategy3_Credit[,2]/100,as.Date(Strategy3_Credit[,1]))
colnames(Strat3_Credit) <- "CreditCheck"

Strat3.HikePeriod.Daily <- hikePeriodData(Strat3_Credit,govt.10Year.daily)

Strat3.Stats <- Necessarystats(Strat3.HikePeriod.Daily,"D")
Strat3.Stats

#Get complete correlations during this period
Strat3.Corr <- lapply(Strat3.HikePeriod.Daily,cor)

Strat3.HikePeriod.Weekly <- weeklyData(Strat3.HikePeriod.Daily)
Strat3.RollCorr <- rollingCorrelations(Filter(Negate(is.null), Strat3.HikePeriod.Weekly),"W")
```

```{r echo=FALSE}
plot(do.call(rbind,Strat2.RollCorr[c("04_06","Recession","Now")]),main="Volatility strategy vs Govt 10 year")
abline(v = as.POSIXct.Date(as.Date(hikePeriods[5,2])), col = 'blue', lty = 3, lwd = 2)
abline(v = as.POSIXct.Date(as.Date(hikePeriods[6,2])), col = 'blue', lty = 3, lwd = 2)
legend("topright",lty=c(1), col=c("black"),c("20Y L, 2*10Y S,1Y L"))
```


##COVARIANCE MATRIX BASED ON WEIGHTS
```{r echo=FALSE}
#Get Risk free rate
factordata <- read.csv("F-F_Research_Data_Factors_daily.csv",skip = 4,header = T,stringsAsFactors = F)
rf <- xts(factordata$RF,ymd(factordata$X))

#Fixed Income
##Barclays Aggregate
BarcTotalAggr <- xts(data$`Barclays US Total Aggregate`[,c(2,3)],data$`Barclays US Total Aggregate`$Date)
BarcTotalAggr.Daily <- diff(BarcTotalAggr[,2])/100
colnames(BarcTotalAggr.Daily) <- "BarcAggr"
BarcTotalAggr.HikePeriods.Daily <- hikePeriodData(BarcTotalAggr.Daily,govt.10Year.daily)[hikePeriodNames]

#Equity
dataEquity <- read.csv("equity_sector_return.csv")
equity.sectors <- xts(dataEquity[-1]/100,ymd(dataEquity$Date)) 
energy.data <- equity.sectors$Enrgy
telecom.data <- equity.sectors$Telcm
health.data <- equity.sectors$Hlth

energy.HikePeriod <- hikePeriodData(equity.sectors$Enrgy,govt.10Year.daily)[hikePeriodNames]
telecom.HikePeriod <- hikePeriodData(equity.sectors$Telcm,govt.10Year.daily)[hikePeriodNames]
health.HikePeriod <- hikePeriodData(equity.sectors$Hlth,govt.10Year.daily)[hikePeriodNames]

#Commodities
dataGold <- read.csv("GOLD_FUTURE.csv")
gold <- xts(dataGold[-1],as.Date(dataGold$Date,"%m/%d/%Y"))
colnames(gold) <- c("Gold")
gold <- (gold - lag(gold))/lag(gold)[-1]
gold.HikePeriod <- hikePeriodData(gold,govt.10Year.daily)[hikePeriodNames]

dataOil <- read.csv("OIL_FUTURE.csv")
oil <- xts(dataOil[-1],as.Date(dataOil$Date,"%m/%d/%Y"))
colnames(oil) <- c("Oil")
oil <- (oil - lag(oil))/lag(oil)[-1]
oil.HikePeriod <- hikePeriodData(oil,govt.10Year.daily)[hikePeriodNames]

#FX
zar.data <- read.csv("ZAR.csv") 
zar <- xts(zar.data$daily.returns,as.Date(zar.data$Index,"%m/%d/%y"))
colnames(zar) <- "ZAR"
zar.HikePeriod <- hikePeriodData(zar,govt.10Year.daily)[hikePeriodNames]

#Calculate
weights <- c(0.1069516,0.2349563,0.3274565,0.1324940,0.1981415)
names(weights) <- hikePeriodNames

#Small cleanup. Barclays Aggregate has only monthly data for 1983-84. So change others
energy.HikePeriod$`83_84` <- apply.monthly(1+energy.HikePeriod$`83_84`,prod)-1
colnames(energy.HikePeriod$`83_84`) <- "Enrgy"
telecom.HikePeriod$`83_84` <- apply.monthly(1+telecom.HikePeriod$`83_84`,prod)-1
colnames(telecom.HikePeriod$`83_84`) <- "Telcm"
health.HikePeriod$`83_84` <- apply.monthly(1+health.HikePeriod$`83_84`,prod)-1
colnames(health.HikePeriod$`83_84`) <- "Hlth"
oil.HikePeriod$`83_84` <- apply.monthly(1+oil.HikePeriod$`83_84`,prod)-1
colnames(oil.HikePeriod$`83_84`) <- "Oil"
gold.HikePeriod$`83_84` <- apply.monthly(1+gold.HikePeriod$`83_84`,prod)-1
colnames(gold.HikePeriod$`83_84`) <- "Gold"
zar.HikePeriod$`83_84` <- apply.monthly(1+zar.HikePeriod$`83_84`,prod)-1
colnames(zar.HikePeriod$`83_84`) <- "ZAR"


##################
#CALCULATECOVCORMATRIX - calculates the covariance matrix of various assets involved
#given weights corresponding to each hike period
#param(weightsPeriods) - Weights for each previous rate hikes.
##################

CalculateCovCorMatrix <- function(weightsPeriods){
  names(weightsPeriods) <- hikePeriodNames
  
  #Get merged data of all assets for all periods
  mergedData <- lapply(names(weightsPeriods),function(period){
      periodMerged <- merge.xts(
                                #BarcTotalAggr.HikePeriods.Daily[[period]]$BarcAggr,
                                energy.HikePeriod[[period]]$Enrgy,
                                telecom.HikePeriod[[period]]$Telcm,
                                health.HikePeriod[[period]]$Hlth,
                                oil.HikePeriod[[period]]$Oil,
                                gold.HikePeriod[[period]]$Gold
                                #,
                                #zar.HikePeriod[[period]]$ZAR
                                )
      na.omit(periodMerged)
    })
  names(mergedData) <- hikePeriodNames
  
  #Weight all returns based on corresponding weight for that period
  mergedData.weighted <- lapply(names(weightsPeriods),function(period){
      weightsPeriods[period]*mergedData[[period]]
    })    
  
  
  #connect all the data, and calculate necessary info
  allData <- do.call(rbind,mergedData.weighted)
  results <- list()
  results$MergedData <- allData
  results$Covariance <- cov(allData)
  results$Correlation <- cor(allData)  
  return(results)
}

```

```{r echo=FALSE}
library(knitr)
CovResults <- CalculateCovCorMatrix(weights)
kable(CovResults$Covariance*250)
```

##BUILDING PORTFOLIO using MVE
```{r echo=FALSE}
ExcessReturns.temp <- merge.xts(CovResults$MergedData,rf/100) %>% na.omit
ExcessReturns <- ExcessReturns.temp - matrix(rep(ExcessReturns.temp$rf/100,ncol(ExcessReturns.temp)),ncol=ncol(ExcessReturns.temp),byrow = T)

ExcessReturns.Avg.Daily <- apply(ExcessReturns,2,mean)[-ncol(ExcessReturns)]
ExcessReturns.Avg.ann <- ExcessReturns.Avg.Daily * 250

SRSq <- t(ExcessReturns.Avg.Daily) %*% chol2inv(chol(CovResults$Covariance)) %*% ExcessReturns.Avg.Daily
SR <- sqrt(SRSq)*sqrt(250)
ClientSD.Ann <- 0.15
ClientSD.Daily <- ClientSD.Ann/sqrt(250)
ClientVar.Daily <- ClientSD.Daily^2

mveKForSd <- sqrt(ClientVar.Daily/SRSq)

weightsOfAssets <- lapply(mveKForSd,function(k){k*chol2inv(chol(CovResults$Covariance))%*%ExcessReturns.Avg.Daily})

temp <- t(weightsOfAssets[[1]])
colnames(temp) <- colnames(ExcessReturns[,-ncol(ExcessReturns)])
kable(temp)
weightsOfAssets.std <- lapply(weightsOfAssets,function(weightForSd){weightForSd/sum(weightForSd)})
returns <- lapply(weightsOfAssets,function(assetweight){t(assetweight)%*%ExcessReturns.Avg.Daily})
returns[[1]]*250
```
$Sharpe Ratio_{MVE} = (R_{avg,exc})' \Sigma R_{avg,exc}$   
where  
$R_{avg,exc}$ is the average excess returns of the assets  
$\Sigma$ is the covariance matrix of the assets


```{r}
#Tactical
dailyReturnOfPortfolio <- ExcessReturns[,-ncol(ExcessReturns)]%*%weightsOfAssets[[1]]
dailyReturnOfPortfolio.xts <- xts(dailyReturnOfPortfolio,index(ExcessReturns))

strat2 <- do.call(rbind,Strat2.HikePeriods.Daily[hikePeriodNames])
compdata <- merge.xts(dailyReturnOfPortfolio.xts,strat2[,1])%>%na.omit
cor(compdata)
```
 