

##Fed Fund Rates  
```{r echo=FALSE}
###### FUND RATES - FRED#############
fundrate.daily <- read.csv("Fred_Effective.csv")
fundrate.daily <- xts(fundrate.daily$DFF,as.Date(fundrate.daily$DATE))
plot(fundrate.daily,main="Daily Fund Rates")
```

```{r echo=FALSE}
fundrate.monthly <- read.csv("Fred_Effective_Month.csv")
fundrate.monthly <- xts(fundrate.monthly$FEDFUNDS,as.Date(fundrate.monthly$DATE))
plot(fundrate.monthly)
```

The daily and monthly rate sort of follows the same trend.  
  
##T-Bills   
##1 Year  
   
*Normal Correlation*
```{r echo = FALSE}
######T-BILL 1 YEAR##########
Tbill.1Y <- read.csv("DTB1YR.csv")
Tbill.1Y[Tbill.1Y$DTB1YR == '.',"DTB1YR"] <- NA
Tbill.1Y <- xts(Tbill.1Y$DTB1YR,as.Date(Tbill.1Y$DATE))
Tbill.1Y <- na.approx(Tbill.1Y)
storage.mode(Tbill.1Y) <- "numeric"
Tbill.1Y.full <- na.omit(merge.xts(fundrate.daily,Tbill.1Y))

#Rolling Correlation
Tbill.1Y.Cor3M <- rollapply(Tbill.1Y.full,60,function(x) cor(x[,1],x[,2]),by.column = FALSE)
Tbill.1Y.Cor1Y <- rollapply(Tbill.1Y.full,240,function(x) cor(x[,1],x[,2]),by.column = FALSE)
Tbill.1Y.Cor2Y <- rollapply(Tbill.1Y.full,480,function(x) cor(x[,1],x[,2]),by.column = FALSE)


#Normal Correlation
cor(Tbill.1Y.full)
```
This high value is expected.  

*Rolling Correlation Across Time*  
```{r echo = FALSE}
#plotting
par(mfrow = c(2,2))
plot(Tbill.1Y,main="Tbill over time")
plot(Tbill.1Y.Cor3M,main="3M rolling correlation")
plot(Tbill.1Y.Cor1Y,main="1Y rolling correlation")
plot(Tbill.1Y.Cor2Y,main="3M rolling correlation")
```

We can see a steady high correlation between the two, except during the latest rate hike period(Correct?Why?)  

*Rolling Correlation During July 1999 - July 2000*  
```{r echo = FALSE}
par(mfrow = c(2,2))
#plot(Tbill.1Y.full['1994-01/1995-02'])
#plot(Tbill.1Y.full['2004-06/2006-08'])
plot(Tbill.1Y['1999-07/2000-07'],main="Tbill over time")
plot(Tbill.1Y.Cor3M['1999-07/2000-07'],main="3M rolling correlation")
plot(Tbill.1Y.Cor1Y['1999-07/2000-07'],main="1Y rolling correlation")
```

Correlation is reducing at the end of rate hike period (Correct?Why?)  
  
##3 Month TBill
*Normal Correlation*    
```{r echo = FALSE}
######T-BILL 3 MONTH##########
Tbill.3M <- read.csv("DTB3.csv")
Tbill.3M[Tbill.3M$DTB3 == '.',"DTB3"] <- NA
Tbill.3M <- xts(Tbill.3M$DTB3,as.Date(Tbill.3M$DATE))
Tbill.3M <- na.approx(Tbill.3M)
storage.mode(Tbill.3M) <- "numeric"
Tbill.3M.full <- na.omit(merge.xts(fundrate.daily,Tbill.3M))

#Roll Correlation - 3 month
Tbill.3M.Cor3M <- rollapply(Tbill.3M.full,60,function(x) cor(x[,1],x[,2]),by.column = FALSE)
Tbill.3M.Cor1Y <- rollapply(Tbill.3M.full,240,function(x) cor(x[,1],x[,2]),by.column = FALSE)
Tbill.3M.Cor2Y <- rollapply(Tbill.3M.full,480,function(x) cor(x[,1],x[,2]),by.column = FALSE)

#Normal Correlation
cor(Tbill.3M.full)
```
This high value is expected.  

*Rolling Correlation Across Time*  
```{r echo = FALSE}
#plotting
par(mfrow = c(2,2))
plot(Tbill.3M,main="Tbill over time")
plot(Tbill.3M.Cor3M,main="3M rolling correlation")
plot(Tbill.3M.Cor1Y,main="1Y rolling correlation")
plot(Tbill.3M.Cor2Y,main="2Y rolling correlation")
```

Correct?Why?  


##Govt 10 year  
*Normal correlation*  
```{r echo = FALSE}
#######GOVT BONDS 10 YEAR######
GovtBond.10Y <- read.csv("BOND10YR.csv")
GovtBond.10Y <- xts(GovtBond.10Y$IRLTLT01USM156N,as.Date(GovtBond.10Y$DATE))
GovtBond.10Y <- na.approx(GovtBond.10Y)
storage.mode(GovtBond.10Y) <- "numeric"
GovtBond.10Y.full <- na.omit(merge.xts(fundrate.monthly,GovtBond.10Y))

#Roll Correlation - 3 month
GovtBond.10Y.Cor3M <- rollapply(GovtBond.10Y.full,60,function(x) cor(x[,1],x[,2]),by.column = FALSE)
GovtBond.10Y.Cor1Y <- rollapply(GovtBond.10Y.full,240,function(x) cor(x[,1],x[,2]),by.column = FALSE)
GovtBond.10Y.Cor2Y <- rollapply(GovtBond.10Y.full,480,function(x) cor(x[,1],x[,2]),by.column = FALSE)

#Normal Correlation
cor(GovtBond.10Y.full)
```
Decently high, but not as high as the low maturity.  
  
*Rolling Correlation Across Time*  
```{r echo = FALSE}
#plotting
par(mfrow = c(2,2))
plot(GovtBond.10Y,main="Tbill over time")
suppressWarnings(plot(GovtBond.10Y.Cor3M,main="3M rolling correlation"))
suppressWarnings(plot(GovtBond.10Y.Cor1Y,main="1Y rolling correlation"))
suppressWarnings(plot(GovtBond.10Y.Cor2Y,main="2Y rolling correlation"))
```

A bit high, but more random.    

*Rolling Correlation During July 1999 - July 2000*  
```{r echo = FALSE}
par(mfrow = c(2,2))
#plot(Tbill.1Y.full['1994-01/1995-02'])
#plot(Tbill.1Y.full['2004-06/2006-08'])
suppressWarnings(plot(GovtBond.10Y.full['1999-07/2000-07'],main="Tbill over time"))
suppressWarnings(plot(GovtBond.10Y.Cor3M['1999-07/2000-07'],main="3M rolling correlation"))
suppressWarnings(plot(GovtBond.10Y.Cor1Y['1999-07/2000-07'],main="1Y rolling correlation")) 
```
Reducing At the end of the rate hike.    
 
##Barclays Aggregate Index
*Normal Correlation*  
```{r echo=FALSE}
########Barclays Aggreggate#######
BarcTotalAggr <- xts(data$`Barclays US Total Aggregate`[,c(2,3)],data$`Barclays US Total Aggregate`$Date)
BarcTotalAggr.full <- na.omit(merge.xts(fundrate.daily,BarcTotalAggr))

#Roll Correlation - 3 month
BarcTotalAggr.Price.Cor3M <- rollapply(BarcTotalAggr.full,60,function(x) cor(x[,1],x[,2]),by.column = FALSE)
BarcTotalAggr.Price.Cor1Y <- rollapply(BarcTotalAggr.full,240,function(x) cor(x[,1],x[,2]),by.column = FALSE)
BarcTotalAggr.Price.Cor2Y <- rollapply(BarcTotalAggr.full,480,function(x) cor(x[,1],x[,2]),by.column = FALSE)

BarcTotalAggr.YTM.Cor3M <- rollapply(BarcTotalAggr.full,60,function(x) cor(x[,1],x[,3]),by.column = FALSE)

#Normal Correlation
cor(BarcTotalAggr.full)
```
  
High correlation with YTW and high negative correlation as price.  

*Rolling Correlation Across Time*  
```{r echo = FALSE}
#plotting
par(mfrow = c(2,2))
suppressWarnings(plot(BarcTotalAggr,main="Aggregate over time"))
suppressWarnings(plot(BarcTotalAggr.Price.Cor3M,main="3M rolling correlation"))
suppressWarnings(plot(BarcTotalAggr.Price.Cor1Y,main="1Y rolling correlation"))
suppressWarnings(plot(BarcTotalAggr.Price.Cor2Y,main="2Y rolling correlation"))
```
  
Negative, but few positives(Correct?Why?)     

*Rolling Correlation During July 1999 - July 2000*  
```{r echo = FALSE}
par(mfrow = c(2,2))
#plot(Tbill.1Y.full['1994-01/1995-02'])
#plot(Tbill.1Y.full['2004-06/2006-08'])
suppressWarnings(plot(BarcTotalAggr['1999-07/2000-07'],main="Aggregate over time"))
suppressWarnings(plot(BarcTotalAggr.Price.Cor3M['1999-07/2000-07'],main="3M rolling correlation"))
suppressWarnings(plot(BarcTotalAggr.Price.Cor1Y['1999-07/2000-07'],main="1Y rolling correlation"))
```
Becoming positive correlation at the end of the rate peak period (Why?Correct?)  
  
##5 Year Govt Inflation bonds  
*Normal Correlation*  
```{r echo=FALSE}
GovtInf.5Y <- xts(data$GovtII5[,2],as.Date(data$GovtII5$Date))
GovtInf.5Y <- GovtInf.5Y[!is.na(index(GovtInf.5Y)),]
GovtInf.5Y.full <- na.omit(merge.xts(fundrate.daily,GovtInf.5Y))

#Roll Correlation - 3 month
GovtInf.5Y.Cor3M <- rollapply(GovtInf.5Y.full,60,function(x) cor(x[,1],x[,2]),by.column = FALSE)
GovtInf.5Y.Cor1Y <- rollapply(GovtInf.5Y.full,240,function(x) cor(x[,1],x[,2]),by.column = FALSE)
GovtInf.5Y.Cor2Y <- rollapply(GovtInf.5Y.full,480,function(x) cor(x[,1],x[,2]),by.column = FALSE)

#Normal Correlation
cor(GovtInf.5Y.full)
```
Correlation is high.    

*Rolling Correlation Across Time*  
```{r echo = FALSE}
#plotting
par(mfrow = c(2,2))
plot(GovtInf.5Y,main="Govt Inflation Bond over time")
plot(GovtInf.5Y.Cor3M,main="3M rolling correlation")
plot(GovtInf.5Y.Cor1Y,main="1Y rolling correlation")
plot(GovtInf.5Y.Cor2Y,main="2Y rolling correlation")
```

Quite a few negatives surprisingly (Why?Correct?)  

*Rolling Correlation During July 1999 - July 2000*    
```{r echo = FALSE}
par(mfrow = c(2,2))
#plot(Tbill.1Y.full['1994-01/1995-02'])
#plot(Tbill.1Y.full['2004-06/2006-08'])
plot(GovtInf.5Y['1999-07/2000-07'],main="Aggregate over time")
plot(GovtInf.5Y.Cor3M['1999-07/2000-07'],main="3M rolling correlation")
plot(GovtInf.5Y.Cor1Y['1999-07/2000-07'],main="1Y rolling correlation")
```
More random than expected.  
 
 
 
```{r}
BarcTotalAggr <- xts(data$`Barclays US Total Aggregate`[,c(2,3)],data$`Barclays US Total Aggregate`$Date)
s
```